---
title: "Supporting Information : Insert title"
author: "J. Doe, J. Doe"
date: ""
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_supp.sty
      
tables: True
link-citations: True
urlcolor : blue

csl: ecology-letters.csl
bibliography: REF_ALL.bib
---

<!--checkpoint package - when present, uses the package, sets up a local
installation of all packages as they existed on the date specified in the
same directory as this file.-->
```{r checkpoint_package, echo=F, warning=F, message=F, results="hide"}
#Include packages used in chunks in this doc, also checkpoint. Packages
#used only in other scripts in the same folder as this script, and sourced
#by this script, need not be inlcuded here because the checkpoint package
#scans for them.
library(checkpoint)
library(xtable)
library(devtools,quietly=T,verbose=F)
library(withr,quietly=T,verbose=F)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```

<!--For installing packages from github. Installs them in the same package 
used by checkpoint. Just replace markers below with the user name and 
package name and tag or branch name as indicated
```{r git_install, echo=F, message=FALSE}
withr::with_libpaths(new=.libPaths()[1],
                     devtools::install_github(repo="<github user name>/<package name>",ref="<tag or branch name or hash>",force=T))
```
-->

<!--Other setup-->
```{r setup, echo=F}
source("./mtime.R") #for use in caching as demo'd below
#add additional setup code here
```

<!--comment these out if not desired-->
\tableofcontents
\listoftables
\listoffigures

<!--DEMO CHUNK: placing data in the "data" folder; caching and mtime-->
```{r load_fake_data, echo=F, cache=T, cache.extra=list(mtime("data/FakeData.csv"))}
#Caching is not really needed here because this chunk will run fast 
#(as will all chunks in this demo with the exception of the checkpoint 
#chunk, which cant be cached), but we include for the sake of a demo. 
#Caching is pretty essential in many real scientific questions - any 
#time your code takes more than a few seconds to run. Getting your 
#dependencies right is VERY important when you use caching, and mtime 
#implements dependency on the last-modified time of an external file.
#Dependencies on variables created in earlier chunks can also be
#included, just put them in the cache.extra list (not using mtime).
d<-read.csv("data/FakeData.csv")
```

<!--DEMO CHUNK: Make and save a figure. I find the knitr facility of 
integrating figures generated within a chunk via plot to be limiting
when one needs to produced publication-quality figures. Also, it does
not produce a separate pdf of the figure. So I make the figure manually
in one chunk and then it can be sucked up and displayed wherever. We
make it here. Save to the "results" folder.-->
```{r make_example_figure, echo=F, results="hide"}
pdf(file="results/testfig.pdf")
plot(d$x,d$y,xlab="x",ylab="y")
dev.off()
```

# Data \label{sect:dat} 
<!--I usually label sections starting with sect:, figures starting with
fig:, and tables starting with tab:, to decrease chances of multiply defined labels-->

\noindent We got some data by measuring $x$ and $y$, they look like this:

<!--DEMO CHUNK: Make a table for the data using xtable. knitr::kable seems limited to me,
latex is unlimited, so consider using xtable for complex tables. Also, this saves the 
table as a separate latex file.-->
```{r xtable_chunk, echo=F, results="asis"}
h<-xtable(d,caption="The data, with $x$ and $y$ measured in some locations.",label="tab:dat")
print(h,file="./results/dattable.tex")
```

<!--Now display the table here-->
\input{./results/dattable.tex}

# Results \label{sect:res}
<!--DEMO of user-defined latex commands, math mode, and inline R code-->
\noindent Commands defined in `head_supp.sty` can be used, e.g., we computed the covariance of $x$ and
$y$ and got $\cov(x,y)=$ `r cov(d$x,d$y)`. The $x$ and $y$ data are from table \ref{tab:dat}.

<!--DEMO of citations - note these labels are defined in REFS_ALL.bib-->
Some earlier authors have done work that I like [@burnham2003_modelselection] so I will cite it
to demonstrate citations. @bjornstadfalck2001 also wrote a useful paper.

We also plotted the data:
<!--DEMO: of displaying a separately created and saved plot. I use latex - you can display 
anything with latex, any way you want. Rmd plotting functionality is also an option but
seems less flexible in some ways.-->
\begin{figure}
\includegraphics[width=5in]{./results/testfig.pdf}
\caption{Scatterplot of the data.}
\label{fig:datplot}
\end{figure}

An identical version of this figure also appears in the main text (figure \ref{MT-fig:mtversion}),
although that makes no narrative sense, just to demo the ability to cite a main text figure
from the supporting information (just prepend "MT-" to the reference callout).

# Discussion

\noindent Discuss important things here.

# References
